\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

\section{Implicit assumptions in the maximum-entropy method}

@@

 These studies strive for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? These questions 
**********
\mynote{Version 1}
The present note has three nested purposes.

>>>>

%\section{Implicit assumptions in the maximum-entropy method}
\section{Introduction}

@@

 Using the pairwise \me\ models many studies strived for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]?

Here we show that there is a
contradiction in applying \me\ to the observed data \enquote{representative random sample}
of neurons to generate a \enquote{maximally noncommital} distribution for
that sample.

 \mynote{Version 1}
The present note has three nested purposes.
